Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
include corollary to theorem for g0 main theorem

All such base cases satisfy all of the hypotheses of
Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
generated up to degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}.
It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
(d) that the relations are generated up to degree $2e$.
\end{proof}

>>>>

All such base cases satisfy all of the hypotheses of Theorem
~\ref{thm:ram_order_ind} and their corresponding $R' := R(\sx',
\Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
$e' := \max(5, e_1', \ldots, e_r')$ with relations generated up to
degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
from induction using Theorem ~\ref{thm:ram_order_ind}(b) and
Corollary ~ \ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
\halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
It also follows from induction on Theorem ~\ref{thm:ram_order_ind}(c)
and ~\ref{cor:raise-stacky-order} that the relations are generated
up to degree $2e$.
 \end{proof}
